Memory for television episodes preserves event content while introducing new across-event similarities

### 2020-02-05 paper/main.tex

Statistical models of memory studies often treat recall success as binary (i.e., an item either was or was not recalled), or occasionally categorical \citep[e.g., to distinguish familiarity from recollection;][]{YoneEtal02}.  Such approaches are tenable in classical list-learning or recognition memory paradigms, as the presented stimuli tend to be very simple (e.g., a sequence of individual words or items).  However, the feature-rich content of a naturalistic experiences may later be described with many, highly variable levels of success.  Our framework produces a content-based model of individual stimulus and recall events, allowing for direct quantitative comparison between all stimulus and recall events, as well as between the recall events themselves.  Leveraging these content-based models of the stimulus/recall events, we developed two novel, \textit{continuous} metrics for quantifying naturalistic memory representations:~\textit{precision} and \textit{distinctiveness}.  We define precision as the ``completeness" of recall, or how fully the presented content was recapitulated in memory.  Under our framework, we quantify this for a given recall event as the correlation between the topic proportions of the recall event and the maximally correlated video event (Fig.~\ref{fig:precision-distinctiveness}).  A second novel metric we introduce here is \textit{distinctiveness}, which we define as the ``specificity" of recall, or how unique the description of a given section of content was, compared to descriptions for other sections of content.  We quantify this for each recall event as 1 minus the average correlation between the given recall event and all other recall events not matched to the same video event.  In addition to individual events, one may also use these metrics to describe each participant's overall performance (i.e., by averaging across a participant's event-wise precision or distinctiveness scores).  Participants whose recall events are more veridical descriptions of what happened in the video event will presumably have higher precision scores. We find that, across participants, a higher precision score is correlated to both hand-annotated memory performance (Pearson's $r(15) = 0.56, p = 0.021$) and the number of recall events estimated by our model (Pearson's $r(15) = 0.85, p < 0.001$).  We also hypothesized that participants who recounted events in a more distinctive way would display better overall memory.  We find that this distinctiveness score is related to our model's estimated number of recalled events (Pearson's $r(15) = 0.53, p = 0.028$), and while we do not find distinctiveness to be related to hand-annotated memory performance (Pearson's $r(15) = 0.28, p = 0.275$), this is not entirely surprising given how the hand-annotated memory scores were computed (see \textit{Methods}).

\begin{figure}[t]
  \centering
  \includegraphics[width=1\textwidth]{figs/precision_detail}
  \caption{\small \textbf{Precision metric reflects completeness of recall.} \textbf{A.} Recall precision distributions over participants, for each video event.  Grey violin plots display kernel density estimates for the distribution of recall precision scores for a single video event.  Colored dots within the violin plots represent individual participants' recall precision for that event.  Video events are ordered along the $x$-axis by the average precision with which they were remembered.  \textbf{B.} The set of ``Narrative Details" video annotations (generated by \citealp{ChenEtal17}) for scenes comprising an example video event (22) identified by the HMM.  Each action or feature is highlighted in a different color.  \textbf{C.} A subset of the sentences comprising the most precise (P17) and least precise (P6) participants' recalls of video event 22.  Descriptions of specific actions or features reflecting those highlighted in panel B are highlighted in the corresponding color.}
  \label{fig:precision-detail}
\end{figure}

\begin{figure}[t]
  \centering
  \includegraphics[width=1\textwidth]{figs/distinctiveness_detail}
  \caption{\small \textbf{Distinctiveness metric reflects specificity of recall.} \textbf{A.} Recall distinctiveness distributions over participants, for each video event.  Kernel density estimates for each video event's distribution of recall distinctiveness scores, analogous to Fig.~\ref{fig:precision-detail}A.  \textbf{B.} The set of ``Narrative Details" video annotations (generated by \citealp{ChenEtal17}) for scenes comprising an example video event (19) identified by the HMM.  \textbf{C.} The sentences comprising the most distinctive (P13) and least distinctive (P11) participants' recalls of video event 19.  Descriptions of recalled content specific to video event 19 (as opposed to that combining surrounding events) are highlighted.}
  \label{fig:distinctiveness-detail}
\end{figure}

@@

The prior analyses leverage the correspondence between the 100-dimensional topic proportion matrices for the video and participants' recalls to characterize recall.  However, it is difficult to gain deep insights into that content solely by examining the topic proportion matrices (e.g., Figs.~\ref{fig:model}A, D) or the corresponding correlation matrices (Figs.~\ref{fig:model}B, E, \corrmats).  To visualize the time-varying high-dimensional content in a more intuitive way~\citep{HeusEtal18a} we projected the topic proportions matrices onto a two-dimensional space using Uniform Manifold Approximation and Projection~\citep[UMAP; ][]{McInEtal18}.  In this lower-dimensional space, each point represents a single video or recall event, and the distances between the points reflect the distances between the events' associated topic vectors (Fig.~\ref{fig:trajectory}). In other words, events that are near to each other in this space are more semantically similar.

\begin{figure}[tp]
\centering
\includegraphics[width=1\textwidth]{figs/trajectory}
\caption{\small \textbf{Trajectories through topic space capture the dynamic content of the video and recalls.}  All panels: the topic proportion matrices have been projected onto a shared two-dimensional space using UMAP.  \textbf{A.} The two-dimensional topic trajectory taken by the episode of \textit{Sherlock}.  Each dot indicates an event identified using the HMM (see \textit{Methods}); the dot colors denote the order of the events (early events are in red; later events are in blue), and the connecting lines indicate the transitions between successive events.  \textbf{B.} The average two-dimensional trajectory captured by participants' recall sequences, with the same format and coloring as the trajectory in Panel A.  To compute the event positions, we matched each recalled event with an event from the original video (see \textit{Results}), and then we averaged the positions of all events with the same label.  The arrows reflect the average transition direction through topic space taken by any participants whose trajectories crossed that part of topic space; blue denotes reliable agreement across participants via a Rayleigh test ($p < 0.05$, corrected).  \textbf{C.} The recall topic trajectories (gray) taken by each individual participant (P1--P17).  The video's trajectory is shown in black for reference.  (Same format and coloring as Panel A.)}
\label{fig:trajectory}
\end{figure}
% ------ NOTE: ------
% will update trajectory fig when new version is finished
% - Paxton

Visual inspection of the video and recall topic trajectories reveals a striking pattern.  First, the topic trajectory of the video (which reflects its dynamic content; Fig.~\ref{fig:trajectory}A) is captured nearly perfectly by the averaged topic trajectories of participants' recalls (Fig.~\ref{fig:trajectory}B).  To assess the consistency of these recall trajectories across participants, we asked: given that a participant's recall trajectory had entered a particular location in topic space, could the position of their \textit{next} recalled event be predicted reliably?  For each location in topic space, we computed the set of line segments connecting successively recalled events (across all participants) that intersected that location (see \textit{Methods} for additional details).  We then computed (for each location) the distribution of angles formed by the lines defined by those line segments and a fixed reference line (the $x$-axis).  Rayleigh tests revealed the set of locations in topic space at which these across-participant distributions exhibited reliable peaks (blue arrows in Fig.~\ref{fig:trajectory}B reflect significant peaks at $p < 0.05$, corrected).  We observed that the locations traversed by nearly the entire video trajectory exhibited such peaks.  In other words, participants exhibited similar trajectories that also matched the trajectory of the original video (Fig.~\ref{fig:trajectory}C).  This is especially notable when considering the fact that the number of events participants recalled (dots in Fig.~\ref{fig:trajectory}C) varied considerably across people, and that every participant used different words to describe what they had remembered happening in the video.  Differences in the numbers of remembered events appear in participants' trajectories as differences in the sampling resolution along the trajectory.  We note that this framework also provides a means of detangling classic ``proportion recalled'' measures (i.e., the proportion of video events referenced in participants' recalls) from participants' abilities to recapitulate the full shape of the original video (i.e., the similarity in the shape of the original video trajectory and that defined by each participant's recounting of the video).

Because our analysis framework projects the dynamic video content and participants' recalls onto a shared topic space, and because the dimensions of that space are known (i.e., each topic dimension is a set of weights over words in the vocabulary; Fig.~\topics), we can examine the topic trajectories to understand which specific content was remembered well (or poorly).  For each video event, we can ask: what was the average correlation (across participants) between the video event's topic vector and the closest matching recall event topic vectors from each participant? This yields a single correlation coefficient for each video event, describing how closely participants' recalls of the event tended to reliably capture its content (Fig.~\ref{fig:topics}A).  Given this summary of which events were recalled reliably (or not), we next asked whether the better-remembered or worse-remembered events tended to reflect particular topics.  We computed a weighted average of the topic vectors for each video event, where the weights reflected how reliably each event was recalled.  To visualize the result, we created a ``wordle'' image~\citep{MuelEtal18} where words weighted more heavily by better-remembered topics appear in a larger font (Fig.~\ref{fig:topics}B, green box).  Across the full video, content that reflected topics necessary to convey the central focus of the video (e.g., the names of the two main characters, ``Sherlock" and ``John", and the address of a major recurring location, ``221B Baker Street") were best remembered.  An analogous analysis revealed which themes were poorly remembered.  Here in computing the weighted average over events' topic vectors, we weighted each event in \textit{inverse} proportion to how well it was remembered (Fig.~\ref{fig:topics}B, red box).  The least well-remembered video content reflected information not necessary to conveying the video's ``gist," such as the proper names of relatively minor characters (e.g., ``Mike," ``Molly," and ``Lestrade") and locations (e.g., ``St. Bartholomew's Hospital"), as well as the brief, animated clip participants viewed at the beginning of each of the two scan session (involving ``singing" ``cartoon" characters).

\begin{figure}[tp]
\centering
\includegraphics[width=1\textwidth]{figs/topics}
\caption{\small \textbf{Transforming experience into memory.} \textbf{A.} Average correlations (across participants) between the topic vectors from each video event and the closest-matching recall events.  Error bars denote bootstrap-derived across-participant 95\% confidence intervals.  The stars denote the three best-remembered events (green) and worst-remembered events (red).  \textbf{B.} Wordles comprising the top 200 highest-weighted words reflected in the weighted-average topic vector across video events.  Green: video events were weighted by how well the topic vectors derived from recalls of those events matched the video events' topic vectors (Panel A).  Red: video events were weighted by the inverse of how well their topic vectors matched the recalled topic vectors.  \textbf{C.}  The set of all video and recall events is projected onto the two-dimensional space derived in Figure~\ref{fig:trajectory}.  The dots outlined in black denote video events (dot size reflects the average correlation between the video event's topic vector and the topic vectors from the closest matching recalled events from each participant; bigger dots denote stronger correlations).  The dots without black outlines denote recalled events.  All dots are colored using the same scheme as Figure~\ref{fig:trajectory}A.  Wordles for several example events are displayed (green: three best-remembered events; red: three worst-remembered events).  Within each circular wordle, the left side displays words associated with the topic vector for the video event, and the right side displays words associated with the (average) recall event topic vector, across all recall events matched to the given video event.}
\label{fig:topics}
\end{figure}
% ------ NOTE: ------
% will also update this fig when new version is finished
% - Paxton

A similar result emerged from assessing the topic vectors for individual video and recall events (Fig.~\ref{fig:topics}C).  Here, for each of the three best- and worst-remembered video events, we have constructed two wordles: one from the original video event's topic vector (left) and a second from the average recall topic vector for that event (right).  The three best-remembered events (circled in green) correspond to scenes important to the central plot-line: a mysterious figure spying on John in a phone booth; John and Sherlock discussing the murders in their apartment; and Sherlock laying a trap to catch the murderer.  Meanwhile, the three worst-remembered events (circled in red) reflect scenes that are non-essential to summarizing the narrative's structure: the two appearances of singing cartoon characters; Molly watching as Sherlock beats a corpse in the morgue; and Sherlock noticing evidence of Anderson's and Donovan's affair.

The results thus far inform us about which aspects of the dynamic content in the episode participants watched were preserved or altered in participants' memories of the episode.  We next carried out a series of analyses aimed at understanding which brain structures might implement these processes.  In one analysis we sought to identify which brain structures were sensitive to the video's dynamic content, as characterized by its topic trajectory.  Specifically, we used a searchlight procedure to identify the extent to which each cluster of voxels exhibited a timecourse of activity (as the participants watched the video) whose temporal correlation matrix matched the temporal correlation matrix of the original video's topic proportions (Fig.~\ref{fig:model}B).  As shown in Figure~\ref{fig:brainz}A, the analysis revealed a network of regions including bilateral frontal cortex and cingulate cortex, suggesting that these regions may play a role in processing information relevant to the narrative structure of the video.  In a second analysis, we sought to identify which brain structures' responses (while viewing the video) reflected how each participant would later \textit{recall} the video.  We used an analogous searchlight procedure to identify clusters of voxels whose temporal correlation matrices reflected the temporal correlation matrix of the topic proportions for each individual's recalls (Figs.~\ref{fig:model}D, \corrmats).  As shown in Figure~\ref{fig:brainz}B, the analysis revealed a network of regions including the ventromedial prefrontal cortex (vmPFC), anterior cingulate cortex (ACC), and right medial temporal lobe (rMTL), suggesting that these regions may play a role in transforming each individual's experience into memory.  In identifying regions whose responses to ongoing experiences reflect how those experiences will be remembered later, this latter analysis extends classic \textit{subsequent memory analyses}~\citep[e.g.,][]{PallWagn02} to domain of naturalistic stimuli.
% ------ NOTE: ------
% Searchlight results and figure need to be updated once analysis is re-run
% - Paxton

\begin{figure}[t]
\centering
\includegraphics[width=1\textwidth]{figs/searchlights}
\caption{\small \textbf{Brain structures that underlie the transformation of experience into memory.} \textbf{A.} We searched for regions whose responses (as participants watched the video) matched the temporal correlation matrix of the video topic proportions.  These regions are sensitive to the narrative structure of the video.  \textbf{B.} We searched for regions whose responses (as participants watched the video) matched the temporal correlation matrix of the topic proportions derived from each individual's later recall of video.  These regions are sensitive to how the narrative structure of the video is transformed into a memory of the video.  Both panels: the maps are thresholded at $p < 0.05$, corrected.}
\label{fig:brainz}
\end{figure}

\begin{figure}[t]
\centering
\includegraphics[width=1\textwidth]{figs/neurosynth_decoding}
\caption{\small \textbf{INSERT CAPTION HERE}}
\label{fig:brainz}
\end{figure}
\FloatBarrier

>>>>

Statistical models of memory studies often treat recall success as binary (i.e., an item either was or was not recalled), or occasionally categorical \citep[e.g., to distinguish familiarity from recollection;][]{YoneEtal02}.  Such approaches are tenable in classical list-learning or recognition memory paradigms, as the presented stimuli tend to be very simple (e.g., a sequence of individual words or items).  However, the feature-rich content of a naturalistic experiences may later be described with many, highly variable levels of success.  Our framework produces a content-based model of individual stimulus and recall events by projecting the dynamic content of the video and participants' recalls into a shared topic space.  This allows for direct, quantitative comparison between all stimulus and recall events, as well as between the recall events themselves.  Leveraging these content-based models of the stimulus/recall events, we developed two novel, \textit{continuous} metrics for analyzing naturalistic memory:~\textit{precision} and \textit{distinctiveness}.  We define precision as the ``completeness" of recall, or how fully the presented content was recapitulated in memory.  Under our framework, we quantify this for a given recall event as the correlation between the topic proportions of the recall event and the maximally correlated video event (Fig.~\ref{fig:precision-distinctiveness}).  A second novel metric we introduce here is \textit{distinctiveness}, which we define as the ``specificity" of recall, or how unique the description of a given section of content was, compared to descriptions for other sections of content.  We quantify this for each recall event as 1 minus the average correlation between the given recall event and all other recall events not matched to the same video event.  In addition to individual events, one may also use these metrics to describe each participant's overall performance (i.e., by averaging across a participant's event-wise precision or distinctiveness scores).  Participants whose recall events are more veridical descriptions of what happened in the video event will presumably have higher precision scores. We find that, across participants, a higher precision score is correlated to both hand-annotated memory performance (Pearson's $r(15) = 0.56, p = 0.021$) and the number of recall events estimated by our model (Pearson's $r(15) = 0.85, p < 0.001$).  We also hypothesized that participants who recounted events in a more distinctive way would display better overall memory.  We find that this distinctiveness score is related to our model's estimated number of recalled events (Pearson's $r(15) = 0.53, p = 0.028$), and while we do not find distinctiveness to be related to hand-annotated memory performance (Pearson's $r(15) = 0.28, p = 0.275$), this is not entirely surprising given how the hand-annotated memory scores were computed (see \textit{Methods}).

\begin{figure}[t]
  \centering
  \includegraphics[width=1\textwidth]{figs/precision_detail}
  \caption{\small \textbf{Precision metric reflects completeness of recall.} \textbf{A.} Recall precision by video event.  Grey violin plots display kernel density estimates for the distribution of recall precision scores for a single video event.  Colored dots within each violin plot represent individual participants' recall precision for the given event.  Video events are ordered along the $x$-axis by the average precision with which they were remembered.  \textbf{B.} The set of ``Narrative Details" video annotations (generated by \citealp{ChenEtal17}) for scenes comprising an example video event (22) identified by the HMM.  Each action or feature is highlighted in a different color.  \textbf{C.} A subset of the sentences comprising the most precise (P17) and least precise (P6) participants' recalls of video event 22.  Descriptions of specific actions or features reflecting those highlighted in panel B are highlighted in the corresponding color.}
  \label{fig:precision-detail}
\end{figure}

\begin{figure}[t]
  \centering
  \includegraphics[width=1\textwidth]{figs/distinctiveness_detail}
  \caption{\small \textbf{Distinctiveness metric reflects specificity of recall.} \textbf{A.} Recall distinctiveness by video event.  Kernel density estimates for each video event's distribution of recall distinctiveness scores, analogous to Fig.~\ref{fig:precision-detail}A.  \textbf{B.} The sets of ``Narrative Details" video annotations (generated by \citealp{ChenEtal17}) for scenes comprising video events described by the example participants in panel C.  Each event's text is highlighted in a different color.  \textbf{C.} The sentences comprising the most distinctive (P13) and least distinctive (P11) participants' recalls of video event 19.  Sections of recall describing each each video event in panel B are highlighted with the corresponding color.}
  \label{fig:distinctiveness-detail}
\end{figure}

@@

The prior analyses leverage the correspondence between the 100-dimensional topic proportion matrices for the video and participants' recalls to characterize recall.  However, it is difficult to gain deep insights into the content of (or relationships between) experiences and memories solely by examining these topic proportions (e.g., Figs.~\ref{fig:model}A, D) or the corresponding correlation matrices (Figs.~\ref{fig:model}B, E, \corrmats).  And while we can directly examine the original text underlying these topic vectors (e.g., Figs.~\ref{fig:precision-detail},~\ref{fig:distinctiveness-detail}) to show how relationships between them reflect real-world behavior, this comparison becomes prohibitively cumbersome at larger timescales.  To visualize the time-varying high-dimensional content in a more intuitive way~\citep{HeusEtal18a} we projected the topic proportions matrices onto a two-dimensional space using Uniform Manifold Approximation and Projection~\citep[UMAP; ][]{McInEtal18}.  In this lower-dimensional space, each point represents a single video or recall event, and the distances between the points reflect the distances between the events' associated topic vectors (Fig.~\ref{fig:trajectory}). In other words, events that are nearer to each other in this space are more semantically similar, and those that are farther apart are less so.

\begin{figure}[tp]
\centering
\includegraphics[width=1\textwidth]{figs/trajectory}
\caption{\small \textbf{Trajectories through topic space capture the dynamic content of the video and recalls.}  All panels: the topic proportion matrices have been projected onto a shared two-dimensional space using UMAP.  \textbf{A.} The two-dimensional topic trajectory taken by the episode of \textit{Sherlock}.  Each dot indicates an event identified using the HMM (see \textit{Methods}); the dot colors denote the order of the events (early events are in red; later events are in blue), and the connecting lines indicate the transitions between successive events.  \textbf{B.} The average two-dimensional trajectory captured by participants' recall sequences, with the same format and coloring as the trajectory in Panel A.  To compute the event positions, we matched each recalled event with an event from the original video (see \textit{Results}), and then we averaged the positions of all events with the same label.  The arrows reflect the average transition direction through topic space taken by any participants whose trajectories crossed that part of topic space; blue denotes reliable agreement across participants via a Rayleigh test ($p < 0.05$, corrected).  \textbf{C.} The recall topic trajectories (gray) taken by each individual participant (P1--P17).  The video's trajectory is shown in black for reference.  Here, events (dots) are colored by their matched video event (Panel A).}
\label{fig:trajectory}
\end{figure}

Visual inspection of the video and recall topic trajectories reveals a striking pattern.  First, the topic trajectory of the video (which reflects its dynamic content; Fig.~\ref{fig:trajectory}A) is captured nearly perfectly by the averaged topic trajectories of participants' recalls (Fig.~\ref{fig:trajectory}B).  To assess the consistency of these recall trajectories across participants, we asked: given that a participant's recall trajectory had entered a particular location in topic space, could the position of their \textit{next} recalled event be predicted reliably?  For each location in topic space, we computed the set of line segments connecting successively recalled events (across all participants) that intersected that location (see \textit{Methods} for additional details).  We then computed (for each location) the distribution of angles formed by the lines defined by those line segments and a fixed reference line (the $x$-axis).  Rayleigh tests revealed the set of locations in topic space at which these across-participant distributions exhibited reliable peaks (blue arrows in Fig.~\ref{fig:trajectory}B reflect significant peaks at $p < 0.05$, corrected).  We observed that the locations traversed by nearly the entire video trajectory exhibited such peaks.  In other words, participants exhibited similar trajectories that also matched the trajectory of the original video (Fig.~\ref{fig:trajectory}C).  This is especially notable when considering the fact that the number of events participants recalled (dots in Fig.~\ref{fig:trajectory}C) varied considerably across people, and that every participant used different words to describe what they had remembered happening in the video.  Differences in the numbers of remembered events appear in participants' trajectories as differences in the sampling resolution along the trajectory.  We note that this framework also provides a means of disentangling classic ``proportion recalled'' measures (i.e., the proportion of video events described in participants' recalls) from participants' abilities to recapitulate the overall unfolding of the original video's content (i.e., the similarity between the shapes of the original video trajectory and that defined by each participant's recounting of the video).
% ------ NOTE: ------
% not sure it's accurate to use "topic space" in paragraph above.  These analyses were all conducted in the 2D manifold space
% - Paxton

The results displayed in Figures \ref{fig:list-learning}C and \ref{fig:precision-detail}A suggest that certain events were remembered better than others.  Given this, we next asked asked whether the events were generally remembered well or poorly tended to reflect particular content.  Because our analysis framework projects the dynamic video content and participants' recalls into a shared space, and because the dimensions of that space represent topics (which are, in turn, sets of weights over words in the vocabulary), we are able to recover the weighted combination of words that make up any point (i.e., topic vector) in this space.  We first computed the average precision with which participants recalled each of the 30 video events (Fig.~\ref{fig:topics}A; note that this result is analogous to a serial position curve created from our continuous recall quality metric).  We then computed a weighted average of the topic vectors for each video event, where the weights reflected how reliably each event was recalled.  To visualize the result, we created a ``wordle'' image~\citep{MuelEtal18} where words weighted more heavily by better-remembered topics appear in a larger font (Fig.~\ref{fig:topics}B, green box).  Across the full video, content that reflected topics necessary to convey the central focus of the video (e.g., the names of the two main characters, ``Sherlock" and ``John", and the address of a major recurring location, ``221B Baker Street") were best remembered.  An analogous analysis revealed which themes were poorly remembered.  Here in computing the weighted average over events' topic vectors, we weighted each event in \textit{inverse} proportion to how well it was remembered (Fig.~\ref{fig:topics}B, red box).  The least well-remembered video content reflected information not necessary to later convey a general summary of the video, such as the proper names of relatively minor characters (e.g., ``Mike," ``Molly," and ``Lestrade") and locations (e.g., ``St. Bartholomew's Hospital").
%, as well as the brief, animated clip participants viewed at the beginning of each of the two scan session (involving ``singing" ``cartoon" characters).

\begin{figure}[tp]
\centering
\includegraphics[width=1\textwidth]{figs/topics}
\caption{\small \textbf{Transforming experience into memory.} \textbf{A.} Average precision (video event-recall event topic vector correlation) across participants for each video event.  Error bars denote bootstrap-derived across-participant 95\% confidence intervals.  The stars denote the three best-remembered events (green) and worst-remembered events (red).  \textbf{B.} Wordles comprising the top 200 highest-weighted words reflected in the weighted-average topic vector across video events.  Green: video events were weighted by how well the topic vectors derived from recalls of those events matched the video events' topic vectors (Panel A).  Red: video events were weighted by the inverse of how well their topic vectors matched the recalled topic vectors.  \textbf{C.}  The set of all video and recall events is projected onto the two-dimensional space derived in Figure~\ref{fig:trajectory}.  The dots outlined in black denote video events (dot size reflects the average correlation between the video event's topic vector and the topic vectors from the closest matching recalled events from each participant; bigger dots denote stronger correlations).  The dots without black outlines denote recalled events.  All dots are colored using the same scheme as Figure~\ref{fig:trajectory}A.  Wordles for several example events are displayed (green: three best-remembered events; red: three worst-remembered events).  Within each circular wordle, the left side displays words associated with the topic vector for the video event, and the right side displays words associated with the (average) recall event topic vector, across all recall events matched to the given video event.}
\label{fig:topics}
\end{figure}

A similar result emerged from assessing the topic vectors for individual video and recall events (Fig.~\ref{fig:topics}C).  Here, for each of the three best- and worst-remembered video events, we have constructed two wordles: one from the original video event's topic vector (left) and a second from the average recall topic vector for that event (right).  The three best-remembered events (circled in green) correspond to scenes important to the central plot-line: a mysterious figure spying on John in a phone booth; John meeting Sherlock at Baker St. to discuss the murders; and Sherlock laying a trap to catch the killer.  Meanwhile, the three worst-remembered events (circled in red) reflect scenes that are non-essential to summarizing the narrative's structure: the video of singing cartoon characters participants viewed prior to the main episode; John asking Molly about Sherlock's habit of over-analyzing people; and Sherlock noticing evidence of Anderson's and Donovan's affair.

The results thus far inform us about which aspects of the dynamic content in the episode participants watched were preserved or altered in participants' memories of the episode.  We next carried out a series of analyses aimed at understanding which brain structures might facilitate these preservations and alterations as the explicit content of the video was transformed into participants' memories.  In one analysis we sought to identify brain structures that were sensitive to the dynamic unfolding of the video's content, as characterized by its topic trajectory.  Specifically, we used a searchlight procedure to identify clusters of voxels whose proximal temporal correlation matrix of activity (as participants watched the video) matched the proximal temporal correlation matrix of original video's topic proportions (Fig.~\ref{fig:brainz}A; see \textit{Methods} for additional details).  We then performed a phase shift-based permutation correction to ensure our searchlight procedure identified regions specifically sensitive to the temporal structure of the video (i.e., rather than those with an autocorrelation length similar to the video; see \textit{Methods}).  We $z$-scored the searchlight results at each voxel against the null distribution of (100) permuted searchlight results, thresholding at $p=0.05$. As shown in Figure~\ref{fig:brainz}C, the analysis revealed a distributed network of regions including \textbf{\textit{????}}, suggesting that these regions may play a role in processing information relevant to the narrative structure of the video.  In a second analysis, we sought to identify which brain structures' responses (while viewing the video) reflected how each participant would later structure their \textit{recall} of the video.  We used an analogous searchlight procedure and permutation correction to identify clusters of voxels whose proximal temporal correlation matrices reflected the proximal temporal correlation matrix of the topic proportions for each individual's recall (Figs.~\ref{fig:brainz}B; see \textit{Methods} for additional details).  As shown in Figure~\ref{fig:brainz}D, the analysis revealed a network of regions including \textbf{\textit{????}}, suggesting that these regions may play a role in transforming each individual's experience into memory.  In identifying regions whose responses to ongoing experiences reflect how those experiences will be remembered later, this latter analysis extends classic \textit{subsequent memory analyses}~\citep[e.g.,][]{PallWagn02} to domain of naturalistic stimuli.
% ------ NOTE: ------
% Potentially need to fill in ????s with names of structures? But maybe not; better to leave without inference because of neurosynth analysis?
% - Paxton

\begin{figure}[t]
\centering
\includegraphics[width=1\textwidth]{figs/searchlights}
\caption{\small \textbf{Brain structures that underlie the transformation of experience into memory.} \textbf{A.} We isolated the proximal diagonals from the upper triangle of the video correlation matrix, and applied this same diagonal mask to the voxel response correlation matrix for each cube of voxels in the brain. We then searched for brain regions whose activation timeseries consistently exhibited a similar proximal correlational structure to the video model, across participants.  \textbf{B.} We used dynamic time warping \citep{BernClif94} to align each participant's recall timeseries to the TR timeseries of the video.  We then applied the same diagonal mask used in Panel A to isolate the proximal temporal correlations and searched for brain regions whose activation timeseries for an individual consistently exhibited a similar proximal correlational structure to each individual's recall.  \textbf{C.} We identified a network of regions sensitive to the narrative structure of participants' ongoing experience.  The map shown is thresholded at at $p < 0.05$, corrected.  \textbf{D}. We also identified a network or regions sensitive to how individuals would later structure the video's content in their recalls.  The map shown is thresholded at at $p < 0.05$, corrected.}
\label{fig:brainz}
\end{figure}

The set of searchlight analyses described above yielded two distributed networks of brain regions, whose activity timecourses mirrored to the temporal structure of the video (Fig.~\ref{fig:brainz}C) or participants' eventual recalls (Fig.~\ref{fig:brainz}D).  As an exploratory analysis, we sought to identify structures comprised these networks and what functions are shared among them.  To accomplish this in a blind, unbiased manner (i.e., without reverse inference via visual observation) we used \texttt{Neurosynth} \citep{YarkEtal11}.  \texttt{Neurosynth} parses a massive online database of over 14,000 neuroimaging studies and constructs meta-analysis images for over 13,000 psychology- and neuroscience-related terms based on NIfTI images accompanying studies where those terms appear at a high frequency.  Given a novel image tagged with its value type (e.g., $t$-, $F$- or $p$-statistics), \texttt{Neurosynth} can then \textit{decode} the list of terms whose meta-analysis images are most similar.  We constructed brain maps of voxelwise $p$-values derived from our permutation correction (masking voxels with a corresponding permutation-derived $z$-score at or below zero).  These maps describe the extent to which each voxel specifically reflected the temporal structure of the video or individuals' recalls (i.e., for each voxel, the percentage of phase-shifted topic vector correlation matrices to which the voxel activity correlation matrix was less similar).  These $p$-value maps for the video- and recall-driven searchlight analyses are displayed in Figure \ref{fig:neurosynth}, along with the top ten terms decoded from each using \texttt{Neurosynth}.

\begin{figure}[t]
\centering
\includegraphics[width=1\textwidth]{figs/neurosynth_decoding}
\caption{\small \textbf{Decoding distributed statistical maps via Neurosynth meta-analyses.} \textbf{A.} Video-searchlight $p$-map and top 10 decoded terms.  We constructed a map of the permutation-derived $p$-values for the video-driven searchlight analysis (Fig.~\ref{fig:brainz}A, C) for all voxels with a positive permutation-derived $z$-score.  The top 10 terms decoded from this $p$-map are shown in red.  \textbf{B.} Recall-searchlight $p$-map and top 10 decoded terms.  We constructed a map of the permutation-derived $p$-values for the recall-driven searchlight analysis (Fig.~\ref{fig:brainz}B, D) for all voxels with a positive permutation-derived $z$-score.  The top 10 terms decoded from this $p$-map are shown in blue.}
\label{fig:neurosynth}
\end{figure}
\FloatBarrier
